A Detection of the Environmental Dependence of the Stellar Profiles and haloes of Massive Central Galaxies

### 2017-07-13 draft/paper2.tex
Edit results 4

    Our results suggest that: 
    (1) At fixed \mtot{}, central galaxies in more massive haloes tend to have 
    lower fractions of \mstar{} stored in the inner region; 
    (2) For massive galaxies with similar \minn{}, the ones in more massive haloes on 
    average have more prominent outer envelopes. 
    The scientific implication of this result is briefly discussed in 
    Section~\ref{sec:discussion}.
%% ------------------------------------------------------------------------------------ %%

    At the same time, we also find \rbcg{} galaxy tends to have lower \mstar{} within 
    inner 5-10 kpc and shallower inner \mden{} profile than the \nbcg{} one at 
    fixed \mtot{}. 
    Although the HSC images do not have sufficient resolution to investigate this in 
    details, it is worth pointing out that this difference could be physically 
    interesting. 
    Observations of compact quiescent galaxies at high-$z$ often reveal higher 
    \mden{} in the central region than their descendants, and certain process need to  
    be responsible for reducing the central \mden{} (e.g. strong adiabatic expansion 
    induced by powerful AGN feedback; \citealt{Fan2008}).
    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which is 
    common in the assembly history of massive galaxies, can also flatten the central 
    \mden{} profile (e.g. \citealt{Milosavljevi2002}).
    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} galaxies 
    with very low \minn{} at high \mtot{} end that are apparently not bothered by 
    problematic photometry or exceptionally bad seeing.  
    They may be similar to the recently discovered massive BCGs with very large core 
    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) resulting from SMBH mergers.
    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
    topic to investigate in the future.

>>>>

    Our results suggest that: 
    (1) At fixed \mtot{}, central galaxies in more massive haloes tend to have 
    lower fractions of \mstar{} stored in the inner region; 
    (2) For massive galaxies with similar \minn{}, the ones in more massive haloes on 
    average have more prominent outer envelopes. 
    The scientific implication of this result is briefly discussed in 
    Section~\ref{sec:discussion}.

    At the same time, we also find \rbcg{} galaxy tends to have lower \mstar{} within 
    inner 5-10 kpc and shallower inner \mden{} profile than the \nbcg{} one at 
    fixed \mtot{}. 
    Although the HSC images do not have sufficient resolution to investigate this in 
    details, it is worth pointing out that this difference could be physically 
    interesting. 
    Observations of compact quiescent galaxies at high-$z$ often reveal higher 
    \mden{} in the central region than their descendants, and certain process need to  
    be responsible for reducing the central \mden{} (e.g. strong adiabatic expansion 
    induced by powerful AGN feedback; \citealt{Fan2008}).
    Coalesce of super-massive black hoes (SMBHs) at the end of major merger, which is 
    common in the assembly history of massive galaxies, can also flatten the central 
    \mden{} profile (e.g. \citealt{Milosavljevi2002}).
    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} galaxies 
    with very low \minn{} at high \mtot{} end that are apparently not bothered by 
    problematic photometry or exceptionally bad seeing.  
    They may be similar to the recently discovered massive BCGs with very large core 
    (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014}) resulting from SMBH mergers.
    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
    topic to investigate in the future.
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_ell_color_environ}
      \caption{
          Radial variations in ellipticity and optical colors for massive galaxies. 
          The format of this figure is similar to the right hand side of 
          Fig~\ref{fig:prof_1}. 
          Top panels show the ellipticity profile, middle panels show $g-r$, and lower 
          panels show $g-i$. 
          We compare our results with those from \citet{Tal2011} based on stacking 
          large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
          (solid blue line on top panel). 
          We also compare with the results from a stacking analysis of nearby massive 
          galaxies with high concentration index ($C>2.6$) in 
          \citet[][blue dash lines on the top and middle panels]{DSouza2014}. 
          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
          lines on the middle and bottom panels]{LaBarbera2010}.
          }
      \label{fig:ell_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\subsection{Ellipticity and Color Profiles}
    \label{ssec:ell_color}

    We now study how the ellipticities (computed via \texttt{Ellipse}) and $k$-corrected 
    optical colors of massive galaxies vary with radius. 
    We also study whether or these radial trends differ between our various samples. 
    These quantities contain interesting information about the physical processes that 
    shape galaxies, but here we study them mainly with two goals in mind:

        \item To see whether the ellipticity profile depends strongly on environment, 
            and to see whether or not the fact that we use an using average isophotal 
            shape for our our 1-D \mden{} profiles has any impact on our results.

        \item To verify that the average color gradient does not depend strongly on 
            the environment and that is not steep enough to cause a problem with our 
            choice the assumption that it is reasonable to use average \m2l for 
            comparing massive galaxies. 
            We extract color profiles by applying the isophotes in $i$-band to images 
            in other bands in ``forced photometry'' manner.

    We compute ellipticities and color profiles in the radial range of 5-50 kpc 
    (this is the range where we can safely ignore differences in sky subtraction and 
    seeing across different bands). 
    We apply Galactic extinction and $k$-correction to both $g-r$ and $g-i$ color 
    profiles; the $k$-correction values are also from \texttt{iSEDFit} results.
    We show the average ellipticity, $g-r$, and $g-i$ color profiles for the 
    \mtot{}-matched (\minn{}-matched) samples of \rbcg{} and \nbcg{} galaxies on the 
    left (right) side of \ref{fig:ell_color}. 
    We also compare our results with previous work based on stacking SDSS galaxies 
    (e.g. \citealt{LaBarbera2010, Tal2011, DSouza2014}).

    We find that in general, the ellipticities of massive galaxies increases with 
    radius from $e\le 0.2$ around 5-10 kpc to $e{\sim} 0.3$ at 40-50 kpc. 
    This is consistent with previous 2-D modeling results from \citet{Huang2013a}. 
    The ellipticity profiles of the \mtot{}-matched samples are very similar at 
    $r<50$ kpc (2-3$\times R_{\mathrm{e}}$ for their \mstar{}). 
    However, for the \minn{}-matched samples, the \rbcg{} galaxies have higher 
    ellipticity than the \nbcg{} ones at $r > 10$ kpc, while their inner ellipticity 
    profiles are very similar.  
    This further hints that massive central galaxies in different halos but with 
    similar ``in-situ'' mass may experience different late-time merging histories. 
    Overall, the relative low ellipticity value and the fact that the ellipticity 
    gradients are shallow lead us to conclude that the use of an average 
    isophotal ellipticity is fine for this present study.

    Previous attempts to constrain ellipticity gradients have relied on image 
    stacking techniques (e.g. \citealt{Tal2011}, \citealt{DSouza2015}). 
    Compared to our measurements, we find that stacked ellipticity profiles tend to 
    underestimate the ellipticity in the outskirt. 
    Ellipticity profiles contain additional information about the assembly histories 
    and in future work, it would be of interest to compare our ellipticity profiles 
    with predictions from hydrodynamic simulations such as Illustris 
    (\citealt{Vogelsberger2014}, \citealt{Genel2014}) or \textit{Horizon-AGN} 
    (\citealt{Dubois2014}).

    In terms of color gradients, we find shallow and negative gradients of median 
    $g-r$ and $g-i$ color profiles for both \rbcg{} and \nbcg{} galaxies. 
    For both \mtot{}- and \minn{}-matched samples, we find no significant difference
    in their median color profiles, which supports the assumption of using single 
    average \m2l{} value to estimate \mden{} profiles.
    The median $g-r$ color profiles are quite consistent with those based on 
    stacked SDSS images. 
    For the $g-i$ profiles, the HSC ones show steeper gradients than the SDSS ones, 
    however, it is important to point out that the SDSS $i$-band suffers from the 
    so-called ``red-halo'' effect of (e.g. \citealt{Wu2005}, \citealt{Tal2011}) that 
    could make the SDSS color appears redder. 
    In contrast, HSC $i$-band image do not suffer from this effect (thanks to thick 
    CCDs), therefore can help provide more accurate color estimates.
%% ------------------------------------------------------------------------------------ %%
